Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-05-30 WRITEUP/ms.tex
moved comparison of velo disp to Sec 5.1

% ------------------
\section{Numerical Simulations}\label{sec:sim}
The simulations used in this work are described by \citealt{Pallottini17a, Pallottini17b} and are briefly summarized here.
%
\ncode{Serra}\footnote{Greenhouse in Italian.} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) techniques to achieve high spatial resolution in regions of interest (e.g., regions of high density).
%
In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier02a} as the AMR backend. The simulation used here covers a comoving box of 20\,Mpc $h$\pmOne in size. The simulation zooms in on a target halo of mass $M_{\rm DM}\simeq10^{11} \Msun$. The Lagrangian region of the halo (2.1\,Mpc $h$\pmOne) has a dark matter mass resolution of $\simeq 6\times 10^4 \Msun$, equivalent at initial density to a baryonic mass resolution of $1.2 \times 10^4 \Msun$. This region is spatially refined with a quasi-Lagrangian criterion based on a mass threshold, so that a cell is refined if its total (dark+baryionic) mass exceedes the mass resolution by a factor of eight. The finest refined cell allowed in the zoom in region has size $l_{\rm cell}\simeq$\,30\,pc (at $z = 6$), i.e. sizes are comparable to the sizes of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a},
The models include a non-equilibrium chemical network following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$, and H$_2^+$ \citep{Grassi14a,Bovino16a}. Of particular importance here is that abundances are calculated using an on-the-fly non-equilibrium formation of molecular hydrogen scheme described by \citet{Pallottini17a}.

@@

\subsection{Distributions of MCC Basic Properties}

We start by considering the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm gas}} {\left(M_{\rm gas} + M_\star\right)}.
\end{equation}
%
We show in \Fig{dist} the results for the distributions considering all the evolutionary stages and dividing the sample in a low ($n_{\rm cut}$\eq0.32\,\cc, top panels) and a high ($n_{\rm cut}$\eq18.96\,\cc, lower panels) density cuts\footnote{The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure. However, not all evolutionary stages considered have at least one MCC at this highest density threshold, we therefore consider MCCs identified with the second highest density threshold ($n_{\rm cut}$\eq18.96\,\cc).}.
%
Overall, the mass of all MCCs identified ranges between $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun, which is comparable to those observed in \z$\sim$2 galaxies in rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}. The gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,100 over all the MCCs identified across all evolutionary stages of \flower.
% GMCs in nearby galaxies: 10^5 < M < 1e7 Msun \citep{Rosolowsky03a, Freeman17a}
%
The most massive ($M_{\rm gas}>$10$^8$\,\Msun) cloud identified at each density threshold corresponds to the molecular disk of the galaxy, which is identified as a single component for low $n_{\rm cut}$. This main disk component occupy the top right corner of \Fig{stellarRatio16} has a \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} stellar-to-gas mass ratio of $\simeq$\,50--100.

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
\caption{Distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest $n_{\rm cut}$ (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels) over all the considered evolutionary stages. Note that the scales shown on the $y$-axes are different between the top and bottom panels, as fewer MCCs are identified at higher $n_{\rm cut}$.
\label{fig:dist}}
\end{figure*}

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_stellar-to-gas-mass_ss16.png}
\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower.
The most massive MCCs have the highest stellar-to-gas mass ratio ($\gtrsim$\,1) \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} as they correspond to a large part of \flower, and thus,
include a large number of stellar mass that is already ensembled in \flower
\label{fig:stellarRatio16}}
\end{figure}

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/3by2_clumpProp_ss16-ss22.png}
\caption{
Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation
(middle), and $\sigma^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for
MCCs (star symbols) identified in the two most extreme evolutionary
stages of \flower\ --- accreting phase (left) and starburst phase
(right). Star symbols are color-coded by the density thresholds
$n_{\rm cut}$, as illustrated by the colorbar.
Literature data in the linewidth-size plots are from \citet{Heyer04a, Rosolowsky05a, Bolatto08a,
% black dot = extragalactic GMCs in quiescent environments
Leroy15a}, and \citet{Swinbank11a}, and the empirical scaling relations are
from \citet{Larson81a, Heyer04a, Bolatto08a}.
Data points in the $\alpha_{\rm vir}$-mass figure are taken from
\citet{Kauffmann17a} and \citet{Kauffmann17b} and references therein
(see Fig 4 of \citealt{Kauffmann17b}).
The gray dotted lines shown in the bottom panels correspond to the various external pressures for
gas in equilibrium, see Equation~\ref{eqn:v0}.
\label{fig:larsons_single}}
\end{figure*}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/alpha_vir_ss16-ss23.png}
\caption{Virial parameter as a function of MCC mass for different evolutionary stages of \flower, beginning from the accreting phase (top left).
Evolutionary stages are shown chronologically from panels {\it (a)} through {\it (f)}.
Definition of symbols are same as in \Fig{larsons_single}.
Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$.
The virial parameter vary over the $\sim$300\,Myr shown here as \flower\ evolves. Most notably, the biggest MCCs transition from
the unstable region as \flower\ accretes materials to being stable (e.g., panel {\it (c)}), a similar pattern is seen in the pre-starburst through
post-starburst phase.
The variation is clearly seen between the pre-starburst through post-starburst phase.
Excluding the biggest MCCs (see \Fig{stellarRatio16} and \Sec{singless}),
MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. \AP{I still think that this figure might be a bit redundant}
\label{fig:alphaEvol}}
\end{figure*}

@@

We can now focus on the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}). Scaling relations for the MCCs identified are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right panels), respectively.

@@

% middle
While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some of them (see \Fig{stellarRatio16}).
%
MCCs with the highest \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} stellar-to-gas mass ratio ($\gtrsim$\,1) correspond to the central main disk of \flower (see top panels of \Fig{MCC} and \Fig{MCC28}, see also \Sec{distribution}), which includes a large fraction of stellar mass that are already assembled in \flower. This explains the low total virial parameter seen in the most massive MCCs of \flower in this phase, as shown in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influence the overall stability of such MCCs.

% PVE
Motivated by observational studies, we also plot the $\sigma_{\rm gas}^2/R$ ratio and gas surface density of MCCs in the bottom left panels of \Fig{larsons_single}. In the same plot, we show those observed in the Galactic Ring Survey (GRS) of the Milky Way \citep{Heyer09a} for comparison. Dashed lines in the figure show the loci along which the annotated external pressures are needed for any molecular clouds in equilibrium to have certain linewidths for a given set of surface densities (see \Sec{PVE}).
% (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf. Heyer+09).

@@

% Starburst
In the starburst phase, MCC have similar velocity dispersion and sizes as those in the accreting phase; however, the MCCs in the starburst phase span a wider range in gas surface density (bottom panels of \Fig{larsons_single}) and have lower virial parameters, i.e. they more susceptible to collapse. Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase
%
\Fig{alphaEvol} shows that most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand,
the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase.
This is consistent with our physical intuition of gas instability leading to \SF.

@@

We investigate possible variations in the dynamics of the molecular structures of \flower to test the robustness of our results against the
choice of density threshold by adopting different sets of $n_{\rm cut}$ in identifying the MCCs. That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless} dependent on the choice of density thresholds.

The sizes of MCCs are dependent on the choice of $n_{\rm cut}$, and thus, some of the MCCs within the main disk break into multiple sub-MCCs at higher $n_{\rm cut}$.
%
The cluster of points found at the lowest density threshold, occupying the top right corner of the linewidth-size relation in the top left panel of \Fig{alpha16-28}, are broken down into sub-MCCs at the highest density threshold (see top right panel of the same figure\footnote{Note
that while the biggest MCCs are broken into sub-MCCs at higher $n_{\rm cut}$, MCCs identified at lower density in the outskirts of \flower
typically do not reach the density thresholds as $n_{\rm cut}$ increases. Hence, there are fewer MCCs at the highest density threshold.}).
%
These sub-MCCs are smaller in size, and thus, are shifted leftward in the top right panel. In this way, we identify a population of denser molecular structures (see \Fig{MCC}).

@@

\subsection{Importance of Bulk Motions in Measured Velocity Dispersion} \label{sec:rot}

\begin{figure}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-sigma-kms-bulk_sigma-kms-NT} \\
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss28-sigma-kms-bulk_sigma-kms-NT}
\caption{Gas velocity dispersions from bulk motions and turbulent motions of \flower in accreting (top) and
quiescent phase (bottom). The accreting phase (\Fig{MCC}) displays a more disturbed morphology compared to the
quiescent phase, which displays a disk-like morphology (\Fig{MCC28}).
The velocity dispersion from turbulent motions is higher than that from bulk motions for most MCCs in the accreting phase, but
the opposite is true in the quiescent phase. Thus, large-scale motion plays an important role in contributing to the total velocity dispersion.
This implies that the velocity dispersion measured in molecular gas structures from \obs on similar physical scales
should not be taken as direct evidence that these structures at high redshifts are intrinsically more turbulent than those in the local ISM.
% either higher resolution, or properly accounting for large scale motions.
\label{fig:vv}}
\vspace{0.5em}
\end{figure}

The local sound speed of all identified molecular complexes is typically much smaller than their non-thermal (turbulent) velocities,
as non-thermal pressure dominates thermal pressure for dense gas \citep{Pallottini17b}, i.e. $c_s^2 \ll \sigma_{\rm NT}^2$. In particular, the Mach number averaged on the the MCCs distribution at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.
%
This can be further analyzed as follows. In \Fig{vv} we show the gas velocity dispersions from bulk motions versus turbulent motions for MCCs in the accreting and quiescent phase. Recall that \flower displays a disturbed morphology in the accreting phase but a disk-like morphology in the quiescent phase (see \Fig{MCC} and \Fig{MCC28}).
%
Most MCCs in the accreting phase have turbulent velocity dispersions higher than the bulk motion velocity dispersions, whereas the opposite is true in the quiescent phase. In addition, the two velocity dispersion terms are of the same order of magnitude.
% as the two are connected via the Euler equation
\DL{interpretation To be revised ...}
{\em This indicates that gas velocity dispersions observed on similar physical scales and resolutions as presented here have an important contribution from large-scale rotation.}....
%
Hence, the linewidths observed in \highz molecular gas structures on these scales should {\em not} be taken as a direct evidence they are intrinsically more turbulent than those in the local ISM, and the comparison and interpretation of the dynamics of gas structures with local clouds using e.g., the Larson's relations is non-trivial.
\citet{Behrendt16a} draw a similar conclusion using pc-scale resolution simulation: large-scale bulk motions may mimic turbulent velocity dispersion due to beam smearing.

>>>>

% ------------------
\section{Numerical Simulations}\label{sec:sim}
The simulations used in this work are described by \citealt{Pallottini17a, Pallottini17b} and are briefly summarized here.
%
\ncode{Serra}\footnote{Greenhouse in Italian.} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) techniques to achieve high spatial resolution in regions of interest (e.g., regions of high density).
%
In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier02a} as the AMR backend. The simulation used here covers a comoving box of 20\,Mpc $h$\pmOne in size. The simulation zooms in on a target halo of mass $M_{\rm DM}\simeq10^{11} \Msun$. The Lagrangian region of the halo (2.1\,Mpc $h$\pmOne) has a dark matter mass resolution of $\simeq 6\times 10^4 \Msun$, equivalent at initial density to a baryonic mass resolution of $1.2 \times 10^4 \Msun$. This region is spatially refined with a quasi-Lagrangian criterion based on a mass threshold, so that a cell is refined if its total (dark+baryionic) mass exceeds the mass resolution by a factor of eight. The finest refined cell allowed in the zoom in region has size $l_{\rm cell}\simeq$\,30\,pc (at $z = 6$), i.e. sizes are comparable to the sizes of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a},
The models include a non-equilibrium chemical network following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$, and H$_2^+$ \citep{Grassi14a,Bovino16a}. Of particular importance here is that abundances are calculated using an on-the-fly non-equilibrium formation of molecular hydrogen scheme described by \citet{Pallottini17a}.

@@

\subsection{Distributions of MCC Basic Properties and Outlier}
\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
\caption{Distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest 
$n_{\rm cut}$\eq0.32\,\cc (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels) over all the considered evolutionary stages of \flower traced in the simulation. Note that the scales shown on the $y$-axes are different between the top and bottom panels, as fewer MCCs are identified at higher $n_{\rm cut}$.
\label{fig:dist}}
\end{figure*}

We start by considering the MCC distributions in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm gas}} {\left(M_{\rm gas} + M_\star\right)}.
\end{equation}
%
We show in \Fig{dist} the distributions considering all the evolutionary stages of \flower and dividing the sample in a low 
($n_{\rm cut}$\eq0.32\,\cc, top panels) and a high ($n_{\rm cut}$\eq18.96\,\cc, lower panels) density cuts\footnote{The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure. However, not all evolutionary stages considered have at least one MCC at this highest density threshold, we therefore consider MCCs identified with the second highest density threshold ($n_{\rm cut}$\eq18.96\,\cc).}.
%
Overall, the mass of all MCCs identified ranges between $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun, 
whereas the gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,1.

% address the biggest MCC = molecular disk of \flower
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_stellar-to-gas-mass_ss16.png}
\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower with different $n_{\rm cut}$.
The most massive MCC identified at low $n_{\rm cut}$ shows 
a high stellar-to-gas mass ratio ($\gtrsim$\,1) \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} 
and corresponds to the molecular disk of \flower (see also \Fig{vv}). Thus,
it includes a large number of stellar mass that is already assembled in \flower. Such structure is excluded 
in the discussion of MCC dynamics in the remainder of this paper.
\label{fig:stellarRatio16}}
\end{figure}

The most massive ($M_{\rm gas}>$10$^7$\,\Msun) cloud corresponds to the molecular disk of the galaxy (see e.g., \Fig{MCC}), 
which is identified as a single component at low $n_{\rm cut}$. This main disk component occupy the top right corner of \Fig{stellarRatio16}, with a \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} 
stellar-to-gas mass ratio of $\simeq$\,50--100. 
Such structure has velocity dispersion dominated by bulk motions, as shown in \Fig{vv}, where we compare 
the velocity dispersions of MCCs  
resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) 
for the accreting and quiescent phases of \flower.
The accreting phase (\Fig{MCC}) of \flower displays a disturbed morphology compared to the
quiescent phase, which displays a disk-like morphology (\Fig{MCC28}).
Excluding the molecular disk, the velocity dispersions of most MCCs in the accreting phase of \flower 
are dominated by turbulent motions. 
On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs
in the quiescent disk-like phase.

The most massive MCC is excluded in the discussion of MCC dynamics in the remainder of this paper.
Considering only the MCCs identified at the highest density threshold, the mass of MCCs is $\simeq10^{6.5}$\,\Msun.
% GMCs in nearby galaxies: 10^5 < M < 1e7 Msun \citep{Rosolowsky03a, Freeman17a}

\begin{figure}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-sigma-kms-bulk_sigma-kms-NT} \\
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss28-sigma-kms-bulk_sigma-kms-NT}
\caption{Gas velocity dispersions from bulk motions and turbulent motions for MCCs identified in accreting (top) and
quiescent phase (bottom) of \flower across all $n_{\rm cut}$ (same color-coding as \Fig{stellarRatio16}).
The accreting phase (\Fig{MCC}) of \flower displays a more disturbed morphology compared to the
quiescent phase, which displays a disk-like morphology (\Fig{MCC28}).
Velocity dispersion from turbulent motions dominates over bulk motions for most MCCs in the accreting phase. 
On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs
in the quiescent disk-like phase.
\label{fig:vv}}
\vspace{0.5em}
\end{figure}

The local sound speed of all identified molecular complexes is typically much smaller than their non-thermal (turbulent) velocities,
as non-thermal pressure dominates thermal pressure for dense gas \citep{Pallottini17b}, i.e. $c_s^2 \ll \sigma_{\rm NT}^2$. In particular, the Mach number averaged on the the MCCs distribution at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.
%%
%This can be further analyzed as follows. In \Fig{vv} we show the gas velocity dispersions from bulk motions versus turbulent motions for MCCs in the accreting and quiescent phase. Recall that \flower displays a disturbed morphology in the accreting phase but a disk-like morphology in the quiescent phase (see \Fig{MCC} and \Fig{MCC28}).
%%
%Most MCCs in the accreting phase have turbulent velocity dispersions higher than the bulk motion velocity dispersions, whereas the opposite is true in the quiescent phase. In addition, the two velocity dispersion terms are of the same order of magnitude.
%% as the two are connected via the Euler equation

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/3by2_clumpProp_ss16-ss22.png}
\caption{
Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation
(middle), and $\sigma^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for
MCCs (star symbols) identified in the two most extreme evolutionary
stages of \flower\ --- accreting phase (left) and starburst phase
(right). Star symbols are color-coded by the density thresholds
$n_{\rm cut}$, as illustrated by the colorbar.
Literature data in the linewidth-size plots are from \citet{Heyer04a, Rosolowsky05a, Bolatto08a,
% black dot = extragalactic GMCs in quiescent environments
Leroy15a}, and \citet{Swinbank11a}, and the empirical scaling relations are
from \citet{Larson81a, Heyer04a, Bolatto08a}.
Data points in the $\alpha_{\rm vir}$-mass figure are taken from
\citet{Kauffmann17a} and \citet{Kauffmann17b} and references therein
(see Fig 4 of \citealt{Kauffmann17b}).
The gray dotted lines shown in the bottom panels correspond to the various annotated external pressures needed in order for
the gas to be in equilibrium, see Equation~\ref{eqn:v0}.
\label{fig:larsons_single}}
\end{figure*}

@@

%\begin{figure*}[htbp]
%\centering
%\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/alpha_vir_ss16-ss23.png}
%\caption{Virial parameter as a function of MCC mass for different evolutionary stages of \flower, beginning from the accreting phase (top left).
%Evolutionary stages are shown chronologically from panels {\it (a)} through {\it (f)}.
%Definition of symbols are same as in \Fig{larsons_single}.
%Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$.
%The virial parameter vary over the $\sim$300\,Myr shown here as \flower\ evolves. Most notably, the biggest MCCs transition from
%the unstable region as \flower\ accretes materials to being stable (e.g., panel {\it (c)}), a similar pattern is seen in the pre-starburst through
%post-starburst phase.
%The variation is clearly seen between the pre-starburst through post-starburst phase.
%Excluding the biggest MCCs (see \Fig{stellarRatio16} and \Sec{singless}),
%MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. \AP{I still think that this figure might be a bit redundant}
%\label{fig:alphaEvol}}
%\end{figure*}

@@

Here, we focus on the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}). Scaling relations for the MCCs are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right panels), respectively.

@@

% middle
While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some of them (see \Fig{stellarRatio16}).
% 
MCCs with the highest \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} stellar-to-gas mass ratio ($\gtrsim$\,1) correspond to the central main disk of \flower (see top panels of \Fig{MCC} and \Fig{MCC28}, see also \Sec{distribution}), which includes a large fraction of stellar mass that are already assembled in \flower. This explains the low total virial parameter seen in the most massive MCCs of \flower in this phase, as shown in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability of such MCCs.

% PVE
Motivated by observational studies, we also plot the $\sigma_{\rm gas}^2/R$ ratio and gas surface density of MCCs in the bottom left panels of \Fig{larsons_single}. In the same plot, we show those observed in the Galactic Ring Survey (GRS) of the Milky Way \citep{Heyer09a} for comparison. Dashed lines in the figure show the loci along which the annotated external pressures are needed for any molecular clouds in equilibrium to have certain linewidths for a given set of surface densities (see \Sec{PVE}). 
At a given gas surface density, MCCs display a range of $\sigma^2/R$. 
Such variations in $\sigma^2/R$ is observed in GMCs of the Milky Way \citep{Heyer09a}.

If constant column density (Larson's third law) is truly a fundamental properties of molecular clouds, 
% or the roughly linear relationship between $\rho$ and $R$ of MCCs.
one would expect a single point in the $\sigma_{\rm gas}^2/R$--$\Sigma$ relation at a given gas mass surface density $\Sigma$.
The variation in $\sigma^2/R$ with $\Sigma$ seen here suggests that column density is not a fundamental properties of 
molecular clouds. Previous studies suggest that the observed mass-size relation of molecular clouds 
is solely a result of $\rho\propto M R^{-3}$ and may be an artifact of the limited range of 
column densities a specific molecular line tracer is sensitive to \citep[][]{Ballesteros02a, Ballesteros11a}.
%For instance, \citet{Ballesteros02a} show that the density
%of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of
%two-dimensional space; the latter is done in \obs.
%When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given
%line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant.
%They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$
%observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in
%observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
%% since $M$ would then scale as $R^{3}$ (ånd naturally display a linear relationship in $\log M - \log R$ plot).

@@

% Starburst
In the starburst phase, MCCs have similar velocity dispersion and sizes as those in the accreting phase; however, 
MCCs in the starburst phase span a wider range in gas surface density 
(bottom panels of \Fig{larsons_single}) and have lower virial parameters, even
for MCCs with masses $<$\,10$^7$\,\Msun (i.e., excluding the molecular disk of \flower identified).
That is, more MCCs in the starburst phase of \flower are more susceptible to collapse.
%
% Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase.
%\Fig{alphaEvol} shows that most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand,
%the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase.
%This is consistent with our physical intuition of gas instability leading to \SF.

@@

We investigate possible variations in the dynamics of the molecular structures of \flower 
by adopting different sets of $n_{\rm cut}$ % in identifying the MCCs
to test the robustness of our results against the choice of density threshold. 
That is, how sensitive are the structure properties, and thus, the 
results presented in \Sec{singless} dependent on the choice of density thresholds.

The sizes of MCCs are dependent on the choice of $n_{\rm cut}$. 
As mentioned in \Sec{}, the most massive cloud identified at low H$_2$ gas density threshold corresponds to the molecular 
disk of \flower, and is broken down into multiple smaller MCCs at higher 
$n_{\rm cut}$\footnote{That said, there are fewer MCCs at highest $n_{\rm cut}$ than the lowest $n_{\rm cut}$ 
 since there are fewer cells in the simulations with correspondingly high H$_2$ gas densities.}.
%
%For instance, the cluster of points found at the lowest density threshold, 
%occupying the top right corner of the linewidth-size relation in the top left panel of \Fig{alpha16-28}, 
%are broken down into smaller MCCs at the highest density threshold (see top right panel of the same figure\footnote{Note
%that while the biggest MCCs are broken into smaller MCCs at higher $n_{\rm cut}$, 
%MCCs identified at lower density in the outskirts of \flower
%typically do not reach the density thresholds as $n_{\rm cut}$ increases. Hence, there are fewer MCCs at the highest density threshold.}).
%%
%These MCCs are smaller in size, and thus, occupy the leftward in the top right panel.

@@
